---
title: "Talk like a Pirate!"
params: 
  dat1: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This example expands on the previous example, but includes more skill building. Here you will learn:

 - How to parameterize a quarto document
 - Learn about 'parent' and 'child' docs
 - Cycle through child docs with new scripts

# This example is based on the simpler and fabulous example by Margaret Siple: https://github.com/MargaretSiple-NOAA/parameterized-indexing-example

## MadLib Responces

These MadLib responses were generated on `r `Sys.Date()`. 

```{r, echo=FALSE, message=FALSE, error=FALSE, include=FALSE, comment=FALSE}
dat1 <- params$dat1
src <- list() # an empty list to put all of the entry outputs in
for (i in 1:nrow(dat1)) { # cycle through each row of the spreadsheet
  dat <- dat1[i,] # subset data to the row of interest
  # dynamically fill out the madlib template and add output to the list
  src[[i]] <- knitr::knit_expand(
    file = here::here('code2_child_params','template2_child_madlib_responces.qmd'))
}
# below, print the output from the spreadsheet used in the madlib template
```

`r paste(knitr::knit(text = unlist(src)), collapse = '\n')`

<!-- this is a quarto comment! -->

<!-- the below chunk is pulling calling a child doc and must otherwise remain empty-->

```{r child=here::here("code2_child_params", "template2_child_assess.qmd")}
```

